Case study validations of automatic bullet matching

### 2018-11-01 index.Rmd
restructuring ideas

@@

@@

```{r compare-land-to-land, fig.width = 8, fig.height = 4, fig.cap="Density curves of land-to-land similarity scores from cross-correlation (top) and RF scores (bottom). Different colors indicate same source versus different source for each land. RF scores for different source comparisons are generally well below 0.5. Some same-source comparisons are also below 0.5 for RF scores, indicating potential problems with at least one of the lands involved in the comparison."}
all_lands %>% 
  gather(key = "measure", value = "value", ccf, rfscore) %>%
  mutate(measure = factor(measure, levels = c("ccf", "rfscore"),
                          labels = c("Cross-correlation", "RF score")),
         study = paste(study, group1) %>% str_trim() %>% factor(levels = c("Hamby 44", "Phoenix PD", "Houston FSI G1", "Houston FSI G2", "Houston FSI G3"))) %>%
  ggplot(aes(
    x = value, fill = sameland,
    colour = sameland
  )) +
  geom_density(alpha = 0.6) +
  geom_rug(alpha = 0.5/12, show.legend = F) +
  facet_grid(measure ~ study) +
  theme_bw() +
  scale_fill_manual("Same source", values = c("darkgrey", "darkorange")) +
  scale_colour_manual("Same source", values = c("darkgrey", "darkorange")) +
  scale_x_continuous("Land-to-Land scores", limits = c(0, 1)) +
  theme(legend.position = "bottom") +
  geom_hline(yintercept = 0, show.legend = F)
```

@@

<!-- \begin{table}[ht] -->
<!-- \centering -->
<!-- \begin{tabular}{llrrr} -->
<!--   \hline -->
<!--  && \multicolumn{3}{l}{\bf AUC (95\% Conf. Int)}\\ -->
<!-- \bf Study & \bf Set & \bf RF score & \bf Cross-correlation & \bf CMS \\ -->
<!--   \hline -->
<!-- \bf Hamby 44 &  & 0.937 (0.917, 0.957) & 0.916 (0.891, 0.941) & 0.820 (0.787, 0.854) \\ -->
<!-- \bf  Phoenix PD &  & 0.976 (0.957, 0.994) & 0.986 (0.975, 0.996) & 0.879 (0.838, 0.919) \\ -->
<!-- \bf  Houston FSI & Set 1 & 0.991 (0.983, 0.999) & 0.988 (0.979, 0.997) & 0.785 (0.727, 0.842) \\ -->
<!-- \bf  Houston FSI & Set 2 & 0.898 (0.853, 0.943) & 0.902 (0.861, 0.943) & 0.749 (0.684, 0.814) \\ -->
<!-- \bf  Houston FSI & Set 3 & 0.986 (0.973, 0.999) & 0.987 (0.978, 0.997) & 0.911 (0.880, 0.941) \\ -->
<!--    \hline -->
<!-- \end{tabular} -->
<!-- \caption{\svp{Can we turn this into a picture? It's really dense and hard to interpret...}Area under the curve (AUC) for each (set) of the studies for the random forest score, cross-correlation and CMS. Overall the perform on all sets is very good to excellent for cross-correlation and the random forest score.  As seen in the ROC curves, the algorithm performs the least well on set 2 of the Houston FSI study.  At the land level there is no significant difference in prediction power between RF score and cross-correlation.} \label{tab:aucs} -->
<!-- \end{table} -->

>>>>

## Identification Process

@@

## Explain RF score, CC and CMS

\hh{We already have a start on this above, but we should focus on these three measures in more detail.}

\hh{In the result section we should probably also include a discussion of EER and the threshold for EER for the three measures. Another threshold of interest is CMS=6, because that's what FTEs use often. }

@@

```{r compare-land-to-land, fig.width = 8, fig.height = 4, fig.cap="Density curves of land-to-land similarity scores from cross-correlation (top) and RF scores (bottom). Different colors indicate same source versus different source for each land. RF scores for different source comparisons are generally well below 0.5. Some same-source comparisons are also below 0.5 for RF scores, indicating potential problems with at least one of the lands involved in the comparison."}
all_lands %>% 
  gather(key = "measure", value = "value", ccf, rfscore) %>%
  mutate(measure = factor(measure, levels = c("ccf", "rfscore"),
                          labels = c("Cross-correlation", "RF score")),
         study = paste(study, group1) %>% str_trim() %>% factor(levels = c("Hamby 44", "Phoenix PD", "Houston FSI G1", "Houston FSI G2", "Houston FSI G3"))) %>%
  ggplot(aes(
    x = value, fill = sameland,
    colour = sameland
  )) +
  geom_density(alpha = 0.6) +
#  geom_rug(alpha = 0.5/12, show.legend = F) +
  facet_grid(measure ~ study) +
  theme_bw() +
  scale_fill_manual("Same source", values = c("darkgrey", "darkorange")) +
  scale_colour_manual("Same source", values = c("darkgrey", "darkorange")) +
  scale_x_continuous("Land-to-Land scores", limits = c(0, 1), labels = c(0, 0.25, 0.5, 0.75, 1)) +
  theme(legend.position = "bottom") +
  geom_hline(yintercept = 0, show.legend = F)
```

@@
